---
title: "kutnerALSM5e Appendix C Data Sets"
output:
 rmarkdown::html_vignette:
   toc: true
   number_sections: true
bibliography: references.bib
vignette: >
 %\VignetteIndexEntry{kutnerALSM5e Appendix C Data Sets}
 %\VignetteEngine{knitr::rmarkdown}
 %\VignetteEncoding{UTF-8}
---


```{r label = "setup"}
library(kutnerALSM5e)
packageVersion("kutnerALSM5e")
```


Documentation and construction of the provided data sets in
@kutner2005applied.

# Data Set C.1 SENIC

The primary object of the Study on the Efficiency of Nosocomial Infection
Control (**SENIC** Project [@SENIC]) was to determine whether infection
surveillance and control programs have reduced the rates of nosocomial
(hospital-acquired) infection in United States hospitals.  The data set
consists of a random sample of 113 hospitals selected from the original 338
hospital surveyed.

Each line of the data set has an identification number and provides
information on 11 other variable for the single hospital.  The data presented
here are for the 1975-76 study period.  The 12 variables are:

| Variable Number | Variable Name                     | Description                                                                                                                                                  |
| :-              | :----                             | :------                                                                                                                                                      |
| 1               | id                                | Identification Number: 1- 113                                                                                                                                |
| 2               | length_of_stay                    | Average length of stay of all patients in hospital (in days)                                                                                                 |
| 3               | age                               | Average age of patients (in years)                                                                                                                           |
| 4               | infection_risk                    | Average estimated probability of acquiring infection in hospital (in percent)                                                                                |
| 5               | culturing_ratio                   | Ratio of number of cultures performed to number of patients without signs or symptoms of hospital-acquired infection, times 100                              |
| 6               | chest_x_ray_ratio                 | Ratio of number of X-ray performed to number of patients without signs or symptoms of pneumonia, times 100                                                   |
| 7               | number_of_beds                    | Average number of beds in hospital during study period                                                                                                       |
| 8               | medical_school_affiliation        | 1 = Yes, 2 = No                                                                                                                                              |
| 9               | region                            | Geographic Region, where 1 = NE, 2 = NC, 3 = S, 4 = W                                                                                                        |
| 10              | average_daily_census              | Average number of patients in hospital per day during study period                                                                                           |
| 11              | number_of_nurses                  | Average number of full-time equivalent registered and licensed practical nurses during study period (number of full time plus one half the number part time) |
| 12              | available_facilities_and_services | Percent of 35 potential facilities and services that are provided by the hospital                                                                            |

To load the data into R use the following code.


```{r label = "data_c1_data_dict", echo = TRUE, results = "asis"}
SENIC <-
  read.table(
    file = system.file("datasets", "APPENC01.txt", package = "kutnerALSM5e")
  , header = FALSE
  , col.names = c(
      "id"
    , "length_of_stay"
    , "age"
    , "infection_risk"
    , "culturing_ratio"
    , "chest_x_ray_ratio"
    , "number_of_beds"
    , "medical_school_affiliation"
    , "region"
    , "average_daily_census"
    , "number_of_nurses"
    , "available_facilities_and_services"
    )
  )

# Modify the data to make analysis easier
SENIC[["medical_school_affiliation"]] <-
  as.integer(SENIC[["medical_school_affiliation"]] == 1)

SENIC[["region"]] <-
  factor(x = SENIC[["region"]],
         levels = 1:4,
         labels = c("North-East", "North-Central", "South", "West"))

head(SENIC)
```



# References

<div id="refs"></div>

# Session Info

```{r label = "sessioninfo"}
sessionInfo()
```

